Online supplemental material of the article:\\ \vspace{7mm} 'Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming'\\ \vspace{7mm} \normalsize by

### 2020-04-17 Paper/online_supplemental_material/online_material.tex
few edits in captions in online material

\usepackage{listings}
\usepackage{slashbox}
\usepackage{caption}
\captionsetup{font=footnotesize}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=black]{hyperref}

@@

\begin{figure}
\centering
\includegraphics[scale=0.50]{ch5_fig12_Posteriors_gaydata.pdf}
\caption{Posterior mean predictive distributions of the proposed HSGP model, the regular GP model, and the Splines model. 95\% credible intervals are plotted as dashed lines.}
  \label{ch5_fig12_Posteriors_gaydata}
\end{figure}

@@

The Stan model codes for the exact GP, the approximate GP and the splines models of this case study can be found online at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Same-sex-marriage-data}}.

@@

\begin{figure}
\begin{center}
\begin{tabular}{ c c c}
\includegraphics[scale=0.40, trim = 0mm 33mm 35mm 20mm, clip]{ch5_fig15_truefun_exII.pdf} & \hspace{-5mm} \includegraphics[scale=0.40, trim = 19mm 33mm 35mm 20mm, clip]{ch5_fig15_gpfun_exII.pdf} & \hspace{-5mm}\multirow{-5.5}{*}{ \includegraphics[scale=0.35, trim = 150mm 18mm 0mm 10mm, clip]{ch5_fig15_colorbar_vertical_exII.pdf}}\\ 
\includegraphics[scale=0.40, trim = 0mm 18mm 35mm 20mm, clip]{ch5_fig15_bffun_exII.pdf}  & \hspace{-5mm} \includegraphics[scale=0.40, trim = 19mm 18mm 35mm 20mm, clip]{ch5_fig15_spfun_exII.pdf}
\end{tabular}
\end{center}
\caption{(a) Data-generating function. (b) Posterior mean predictive function of the GP model. (c) Posterior mean predictive function of the HSGP model. (d) Posterior mean predictive function of the splines model. Sample points are plotted as circles}
  \label{ch5_fig15_Posteriors_exII}
\end{figure}

\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.36, trim = 1mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorGP_exII.pdf}}
\subfigure{\includegraphics[scale=0.36, trim = 19mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorHSGP_exII.pdf}}
\subfigure{\includegraphics[scale=0.36, trim = 19mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorSP_exII.pdf}}
\subfigure{\includegraphics[scale=0.30, trim = 150mm 5mm 0mm 20mm, clip]{ch5_fig16_error_colorbar_exII.pdf}}
\caption{Error between the data-generating mean function and the posterior mean of the GP (a), HSGP (b) and spline (c) models. Sample points are plotted as circles.}
  \label{ch5_fig16_errors_exII}
\end{figure}

@@

The Stan model codes for the exact GP, the approximate GP and the splines models of this case study can be found online at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_2D-Simulated-data}}.

@@

Figure \ref{ch5_fig18_gpfun_diabetes} shows the posterior mean predictions of probabilities ($p_i$) of the three models, regular GP, HSGP and spline, fitted over the dataset with the 2 input dimensions \textit{Glucose} and \textit{Pregnancy} ($D=2$). The binary observations $y_i$ are also plotted in the plots as colored points. For the HSGP model, $m_1=20$ and $m_2=20$ basis functions for each dimension, respectively, were used, which lead to a total of 400 multivariate basis functions. A boundary factor for each dimension $c_1=4$ and $c_2=4$ were used. For the spline model, 20 knots per dimension were used.
%
\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.37, trim = 5mm 23mm 39mm 20mm, clip]{ch5_fig18_gpfun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.37, trim = 20mm 23mm 39mm 20mm, clip]{ch5_fig18_bffun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.37, trim = 20mm 23mm 39mm 20mm, clip]{ch5_fig18_spfun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.30, trim = 150mm 4mm 2mm 15mm, clip]{ch5_fig18_legend_diabetes.pdf}}
\caption{(a) Posterior mean predictive functions of the GP model. (b) Posterior mean predictive functions of the HSGP model. (c) Posterior mean predictive functions of the spline (SP) model. Samples observations of suffering (red points) and not suffering (blue points) form the disease are plotted.}
  \label{ch5_fig18_gpfun_diabetes}
\end{figure}

@@

The Stan model codes for the exact GP, the approximate GP and the spline models of this case study can be found online at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Diabetes-data}}.

@@

The Stan model code for the approximate GP model of this case study can be found at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Land-use-classification}}.

>>>>

\usepackage{listings}
\usepackage{slashbox}
\usepackage{caption}
\captionsetup{font=footnotesize}
%\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=black]{hyperref}

@@

\begin{figure}
\centering
\includegraphics[scale=0.50]{ch5_fig12_Posteriors_gaydata.pdf}
\caption{Posterior predictive means of the proposed HSGP model, the regular GP model, and the Splines model. 95\% confident intervals are plotted as dashed lines.}
  \label{ch5_fig12_Posteriors_gaydata}
\end{figure}

@@

The Stan model codes for the exact GP, the approximate GP and the splines models of this case study can be found online at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Same-sex-marriage-data}}\,.

@@

\begin{figure}
\begin{center}
\begin{tabular}{ c c c}
\includegraphics[scale=0.40, trim = 0mm 33mm 35mm 20mm, clip]{ch5_fig15_truefun_exII.pdf} & \hspace{-5mm} \includegraphics[scale=0.40, trim = 19mm 33mm 35mm 20mm, clip]{ch5_fig15_gpfun_exII.pdf} & \hspace{-5mm}\multirow{-5.5}{*}{ \includegraphics[scale=0.35, trim = 150mm 18mm 0mm 10mm, clip]{ch5_fig15_colorbar_vertical_exII.pdf}}\\ 
\includegraphics[scale=0.40, trim = 0mm 18mm 35mm 20mm, clip]{ch5_fig15_bffun_exII.pdf}  & \hspace{-5mm} \includegraphics[scale=0.40, trim = 19mm 18mm 35mm 20mm, clip]{ch5_fig15_spfun_exII.pdf}
\end{tabular}
\end{center}
\caption{Data-generating function (a) and posterior predictive mean functions of the GP (b), HSGP (c) and spline (d) models. Sample points are plotted as circles}
  \label{ch5_fig15_Posteriors_exII}
\end{figure}

\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.36, trim = 1mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorGP_exII.pdf}}
\subfigure{\includegraphics[scale=0.36, trim = 19mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorHSGP_exII.pdf}}
\subfigure{\includegraphics[scale=0.36, trim = 19mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorSP_exII.pdf}}
\subfigure{\includegraphics[scale=0.30, trim = 150mm 5mm 0mm 20mm, clip]{ch5_fig16_error_colorbar_exII.pdf}}
\caption{Error between the data-generating function and posterior mean functions of the GP (a), HSGP (b) and spline (c) models. Sample points are plotted as circles.}
  \label{ch5_fig16_errors_exII}
\end{figure}

@@

The Stan model codes for the exact GP, the approximate GP and the splines models of this case study can be found online at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_2D-Simulated-data}}\,.

@@

Figure \ref{ch5_fig18_gpfun_diabetes} shows the posterior mean predictions of probabilities ($p_i$) of the three models, regular GP, HSGP and spline, fitted over the dataset with the 2 input dimensions \textit{Glucose} and \textit{Pregnancy} ($D=2$). The binary observations $y_i$ are also plotted in the plots as colored points. For the HSGP model, $m_1=20$ and $m_2=20$ basis functions for each dimension, respectively, were used, which lead to a total of 400 multivariate basis functions. A boundary factor for each dimension $c_1=4$ and $c_2=4$ were used. For the spline model, 20 knots per dimension were used.
%
\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.37, trim = 5mm 23mm 39mm 20mm, clip]{ch5_fig18_gpfun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.37, trim = 20mm 23mm 39mm 20mm, clip]{ch5_fig18_bffun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.37, trim = 20mm 23mm 39mm 20mm, clip]{ch5_fig18_spfun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.30, trim = 150mm 4mm 2mm 15mm, clip]{ch5_fig18_legend_diabetes.pdf}}
\caption{Posterior predictive mean functions of the GP (a), HSGP (b) and spline (c) models. Samples observations of suffering (red points) and not suffering (blue points) from the disease are plotted.}
  \label{ch5_fig18_gpfun_diabetes}
\end{figure}

@@

The Stan model codes for the exact GP, the approximate GP and the spline models of this case study can be found online at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Diabetes-data}}\,.

@@

The Stan model code for the approximate GP model of this case study can be found at {\small \url{https://github.com/gabriuma/basis_functions_approach_to_GP/tree/master/Paper/Case-study_Land-use-classification}}\,.
